Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-28 paper/paper.tex
pass

\subsection{Step 1: Reverse Engineering}

@@

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks we analyzed. Column ``Name'' shows the name of the attack,
column ``Source'' shows the source where we obtained data to reproduce
the attack (see Section~\ref{subsec:malicious-traffic}), column
``Type'' shows the kind of attack, column ``Protocol'' shows the name
of the protocol explored in the attack, and column ``Ground Truth''
shows the rule options to capture the attack. The rationale for the
selection were (1) to cover attacks with different characteristics,
(2) to cover attacks of various protocols, and (3) to explore
different features of \tname. As for (1), the selection includes
attacks of the following types: Denial-of-Service
(DoS)~\cite{denial-of-service}, Active Reconnaissance
(AREC)~\cite{active-reconnaissance}, Privilege escalation
(PVE)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion}, and Policy Violation
(PV)~\Fix{local-file-inclusion}. Note that the distribution of attacks
is not uniform across protocols as these distributions are not uniform
in practice---http attacks are prevalent.

>>>>

\subsection{Step 1: Reverse Engineering}
\label{sec:reverse-engineering}

@@

\newcommand{\numNonContentAttacks}{5}
\newcommand{\numContentAttacks}{10}

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks we analyzed.  Non-http attacks are listed at the top of the
table whereas http attacks are listed at the bottom. Recall from
Section~\ref{sec:reverse-engineering} that (1) http attacks are
prevalent, (2) most http attacks use only content options, and (3)
most non-http attacks only use field options. We selected from various
sources \numNonContentAttacks\ non-http attacks and
\numContentAttacks\ http attacks. The higher number of http attacks
reflects their popularity. Column ``Name'' shows the name of the
attack, column ``Source'' shows the source where we obtained data to
reproduce the attack (see Section~\ref{subsec:malicious-traffic}),
column ``Type'' shows the kind of attack, column ``Protocol'' shows
the name of the protocol explored in the attack, and column ``Ground
Truth'' shows the rule options to capture the attack. The rationale
for the selection were (1) to cover various kinds of attacks and (2)
to cover attacks of various protocols. Considering (1), the selection
includes attacks of the following types: Denial-of-Service
(DoS)~\cite{denial-of-service}, Active Reconnaissance
(AREC)~\cite{active-reconnaissance}, Privilege escalation
(PESC)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion}, and Policy Violation
(PVE)~\Fix{local-file-inclusion}.
